Test

### 2016-07-22 Berkeley_PD_Stop.Rmd

View(stop_df)
# Split people information and other information
stop_df <- stop_df %>%
  mutate(Other = str_replace_all(Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", "")) %>%
  mutate(Other = str_replace_all(Other, "^[ ,]{0,4}", "")) %>%
  mutate(Other = str_replace(Other, ",$", ""))

OtherInformation <- c("P", "^M$", ", M$", "^M, P$")
stop_df <- stop_df %>%
  mutate(Dispositions = str_replace_all(Dispositions, ))
stop_df <- mutate(stop_df, Dispositions = str_extract_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))

@@

>>>>

# Split people information and other information
stop_df <- stop_df %>%
  mutate(Other = str_replace_all(Dispositions, "[ ,]{0,2}[a-zA-Z0-9]{6}", "")) %>%
  mutate(Other = str_replace_all(Other, "^[ ,]{0,4}", "")) %>%
  mutate(Other = str_replace(Other, ",$", ""))

OtherInformation <- c( "^M$" = "", ", M$" = "", "M, P$" = "", "P[, ]{0,2}" = "", "AR[, ]{0,2}" = "", "IN[, ]{0,2}" = "", "FC[, ]{0,2}" = "", "CO[, ]{0,2}" = "", "MH[, ]{0,2}" = "", "TOW[, ]{0,2}" = "", "0[, ]{0,2}" = "", "00000[, ]{0,2}" = "")
stop_df <- stop_df %>%
  mutate(Dispositions = str_replace_all(Dispositions, OtherInformation))

@@

#mutate dispositions column to only contain six character cases

stop_df <- mutate(stop_df, Dispositions = str_extract_all(stop_df$Dispositions, "[a-zA-Z0-9]{6}"))
#removes empty cases
stop_df <- mutate(stop_df, Dispositions = str_replace_all(stop_df$Dispositions, "character(0)", ""))

View(stop_df)
View(dispositions)
###
